Tool-driven Revolutions in Archaeological Science

### 2018-11-21 analysis/paper/jcaa-paper.Rmd
typos

# Bibliometric analysis of tool-driven change

@@

In our view, merely using R (or similar open source programming languages) to conduct research might not constitute a tool-driven revolutionb by itself, but publicaly sharing the code used for research, as a solution to problems of irreproducibility, could enable revolutionary change. Openly shared code could speed the widespread adoption of the reproducibility are a core tenet of the scientific process, since it frees researchers from the black box that most mouse-driven computers are, and enables researchers to not only rerun the shared analysis, but to gain access to all parameter settings, empowering them to change these and therefore properly evaluate, extend and reuse the published results. As open source languages such as R (and Python) are free to use, and most trustworthy repositories are also free (such as zenodo, osf, figshare, etc.), then even researchers with limited resources anywhere in the world can to contribute equally to the research community by using and sharing code.

@@

On another level, we'd like to point to the _technicity_ of tools, in our case coding. Aud Sissel Hoel and Iris van der Tuin are drawing on Ernst Cassirer's „Form und Technik“ [-@cassirer_form_1930] and Gilbert Simondon's „Du monde d'existence des objets techniques" [-@simondon_mode_1958] to define technicity as a term to describe that technology, i. e. tools and machines respectively, interact with the human and with nature [@hoel_ontological_2013, 188]. Technology is said to own an instrumental kind of logos (Cassierer, see @hoel_ontological_2013, 194) and in analogy to language it exercises a certain measure of agency in mediating between human, nature and technology. The use of a scripting language might exemplify this quite nicely, as it is not just a technological tool, but quite rightly named "language" as well.

>>>>

# Bibliometric analysis of a tool-driven change

@@

In our view, merely using R (or similar open source programming languages) to conduct research might not constitute a tool-driven revolution by itself, but publically sharing the code used for research, as a solution to problems of irreproducibility, could enable revolutionary change. Openly shared code could speed the widespread adoption of reproducibility as a core tenet of the scientific process, since it frees researchers from the black box that most mouse-driven computers are, and enables researchers to not only rerun the shared analysis, but to gain access to all parameter settings, empowering them to change these and therefore properly evaluate, extend and reuse the published results. As open source languages such as R (and Python) are free to use, and most trustworthy repositories are also free (such as zenodo, osf, figshare, etc.), then even researchers with limited resources anywhere in the world can to contribute equally to the research community by using and sharing code.

@@

On another level, we'd like to point to the _technicity_ of tools, in our case coding. Aud Sissel Hoel and Iris van der Tuin are drawing on Ernst Cassirer's „Form und Technik“ [@cassirer_form_1930] and Gilbert Simondon's "Du monde d'existence des objets techniques" [@simondon_mode_1958] to define technicity as a term to describe that technology, i. e. tools and machines respectively, interact with the human and with nature [@hoel_ontological_2013, 188]. Technology is said to own an instrumental kind of logos (Cassierer, see @hoel_ontological_2013, 194) and in analogy to language it exercises a certain measure of agency in mediating between human, nature and technology. The use of a scripting language might exemplify this quite nicely, as it is not just a technological tool, but quite rightly named "language" as well.
